---
title: "Report.Rmd"
author: "Karla Moreno"
date: "February 7, 2018"
output:
  html_document: default
  word_document: default
  pdf_document: default
params:
    scenario_variable: NA
    Week: NA
    Day: NA
always_allow_html: yes
---

# Dynamic Report

#Creating a document that provides comparison of disease modeling scenarios ran in ADSM. 

We created an R Markdown document that would guide the R user to explore the outputs from ADSM by modifying or expanding this basic code. 

#Background about the simulation modeling of infectious diseases

###Describe the population, location, and disease studied, including the baseline mechanisms of transmission and control strategies that are included in each of the scenarios.

##List of scenarios 
In our example below, we will visualize outputs of two scenarios. Scenarios are simulations of disease spread where factors are modified from the baseline scenario in order to better understand its effect on the outbreak characteristics. 

```{r, include=F}
#Global

library("shiny")
library("RSQLite") #to connect to SQLite from R (this is what I am using)
library("DBI") #(this is what I am using)
library("ggplot2")#to do graphs
library("knitr")#to do rmarkdown documents
library("gridExtra") #to do grid.arrange (multiple graphs in one window)
library ("igraph")# to make network graphs (graph.data.frame)
library("reshape") #melt function
library("maps") #to create maps
library("plotly") #to create dynamic plots in r
library("xlsx")
library("leaflet")


setwd("~/CEAH/ADSM_Missy/R code basics")
    
    
       #Daily exposure of a specific iteration
    dex1<-read.csv("ModSim18_CC_Moore_21Late_files/ModSim18_CC_Moore_21Late/daily_exposures_25.csv")
    dex2<-read.csv("ModSim18_CC_Moore_Early_files/ModSim18_CC_Moore_Early/daily_exposures_14.csv")
    dex3<-read.csv("ModSim18_CC_MooreVX_21Late_files/ModSim18_CC_MooreVX_21Late/daily_exposures_4.csv")
    dex4<-read.csv("ModSim18_CC_MooreVx_Early_files/daily_exposures_10.csv")
    
    dex1$Scenario<-c(rep("Late",nrow(dex1)))
    dex2$Scenario<-c(rep("Early",nrow(dex2)))
    dex3$Scenario<-c(rep("Vx Late",nrow(dex3)))
    dex4$Scenario<-c(rep("Vx Early",nrow(dex4)))
    
    dex1$lat<-dex1$S_Lat #to have same labels as maps
    dex1$long<-dex1$S_Lon
    dex2$lat<-dex2$S_Lat
    dex2$long<-dex2$S_Lon
    dex3$lat<-dex3$S_Lat #to have same labels as maps
    dex3$long<-dex3$S_Lon
    dex4$lat<-dex4$S_Lat
    dex4$long<-dex4$S_Lon
    
    Compared_dailyExposures<-rbind(dex1,dex2,dex3,dex4)
    
    #Daily event of a specific iteration
    de1<-read.csv("ModSim18_CC_Moore_21Late_files/ModSim18_CC_Moore_21Late/daily_events_25.csv")
    de2<-read.csv("ModSim18_CC_Moore_Early_files/ModSim18_CC_Moore_Early/daily_events_14.csv")
    de3<-read.csv("ModSim18_CC_MooreVX_21Late_files/ModSim18_CC_MooreVX_21Late/daily_events_4.csv")
    de4<-read.csv("ModSim18_CC_MooreVx_Early_files/daily_events_10.csv")
    
    
    de1$Scenario<-c(rep("Late",nrow(de1)))
    de2$Scenario<-c(rep("Early",nrow(de2)))
    de3$Scenario<-c(rep("Vx Late",nrow(de3)))
    de4$Scenario<-c(rep("Vx Early",nrow(de4)))
    
    Compared_dailyEvents<-rbind(de1,de2,de3,de4)
    
    
    
    Ty<-table(Compared_dailyEvents$Type,Compared_dailyEvents$Reason,Compared_dailyEvents$Scenario)
    Ty<-data.frame(Ty) #ggplot works with data frames
    colnames(Ty)<-c("Veterinary_action", "Var2", "Scenario","Freq")
    
    Transmission<-table(Compared_dailyExposures$Reason,Compared_dailyExposures$Scenario)
    Tran<-data.frame(Transmission) #ggplot works with data frames
    colnames(Tran)<-c("Transmission", "Scenario", "Freq")
    Tran$Transmission[Tran$Transmission==""] <- NA 
    Tran<-na.omit(Tran)
    
    S1farm<-cbind(dex1$Source_ID, dex1$Recipient_ID, dex1$Scenario)
    colnames(S1farm)<-c("SourceID","RecipientID", "Scenario")
    S1farm<-as.data.frame(S1farm)
    
    S2farm<-cbind(dex2$Source_ID, dex2$Recipient_ID, dex2$Scenario)
    colnames(S2farm)<-c("SourceID","RecipientID", "Scenario")
    S2farm<-as.data.frame(S2farm)
    
    S3farm<-cbind(dex3$Source_ID, dex3$Recipient_ID, dex3$Scenario)
    colnames(S3farm)<-c("SourceID","RecipientID", "Scenario")
    S3farm<-as.data.frame(S3farm)
    
    S4farm<-cbind(dex4$Source_ID, dex4$Recipient_ID, dex4$Scenario)
    colnames(S4farm)<-c("SourceID","RecipientID", "Scenario")
    S4farm<-as.data.frame(S4farm)
    
    daily_graphdatprep<-rbind(S1farm,S2farm,S3farm,S4farm)
      
    

      conCCMoore21Late <- dbConnect(RSQLite::SQLite(), "~/CEAH/ADSM_Missy/R code basics/ModSim18_CC_Moore_21Late/ModSim18_CC_Moore_21Late.sqlite3")
      conCCMooreEarly <- dbConnect(RSQLite::SQLite(), "~/CEAH/ADSM_Missy/R code basics/ModSim18_CC_Moore_Early/ModSim18_CC_Moore_Early.sqlite3")
      conCCMooreVX21Late <- dbConnect(RSQLite::SQLite(), "~/CEAH/ADSM_Missy/R code basics/ModSim18_CC_MooreVX_21Late/ModSim18_CC_MooreVX_21Late.sqlite3")
      conCCMooreVxEarly <- dbConnect(RSQLite::SQLite(), "~/CEAH/ADSM_Missy/R code basics/ModSim18_CC_MooreVx_Early/ModSim18_CC_MooreVX_Early.sqlite3")
      
      #Scenario 1

      
      EpiCurve<-dbSendQuery(conCCMoore21Late, statement = paste("SELECT day, Sum(infnU), Sum(detnU)",
                                                                "FROM  Results_dailybyproductiontype r",
                                                                "WHERE 1=1","AND production_type_id is null",
                                                                "and last_day < 1","group by day","order by 1, 2"))
      EpiCur<-dbFetch(EpiCurve)
      
    
      
      #Scenario 2
      
    
      
      EpiCurve<-dbSendQuery(conCCMooreEarly, statement = paste("SELECT day, Sum(infnU), Sum(detnU)",
                                                               "FROM  Results_dailybyproductiontype r",
                                                               "WHERE 1=1","AND production_type_id is null",
                                                               "and last_day < 1","group by day","order by 1, 2"))
      EpiCur2<-dbFetch(EpiCurve)
      
      #Scenario 3
      
      
      EpiCurve<-dbSendQuery(conCCMooreVX21Late, statement = paste("SELECT day, Sum(infnU), Sum(detnU)",
                                                                "FROM  Results_dailybyproductiontype r",
                                                                "WHERE 1=1","AND production_type_id is null",
                                                                "and last_day < 1","group by day","order by 1, 2"))
      EpiCur3<-dbFetch(EpiCurve)
      
      
      #Scenario 4
      
      
      
      EpiCurve<-dbSendQuery(conCCMooreVxEarly, statement = paste("SELECT day, Sum(infnU), Sum(detnU)",
                                                               "FROM  Results_dailybyproductiontype r",
                                                               "WHERE 1=1","AND production_type_id is null",
                                                               "and last_day < 1","group by day","order by 1, 2"))
      EpiCur4<-dbFetch(EpiCurve)
      
    
      #Creating variable scenario per table
      EpiCur$Scenario<-c(rep("Late",nrow(EpiCur)))
      EpiCur2$Scenario<-c(rep("Early",nrow(EpiCur2)))
      EpiCur3$Scenario<-c(rep("Vx Late",nrow(EpiCur3)))
      EpiCur4$Scenario<-c(rep("Vx Early",nrow(EpiCur4)))
      
      
      #Making Master Tables
      EPICURVE<-rbind(EpiCur, EpiCur2, EpiCur3, EpiCur4);colnames(EPICURVE)<-c("day", "sumInfnU", "sumdetnU","Scenario")
      
     
    
    #Scenario 1
      
      
      OutbreakDuration <- dbSendQuery(conCCMoore21Late, statement = paste("SELECT iteration, diseaseduration",
                                                                          "FROM  Results_dailycontrols r",
                                                                          "WHERE 1=1",
                                                                          "AND last_day >0","order by 1"))
      OutDur<-dbFetch(OutbreakDuration)
      
      
      #Scenario 2
      
      OutbreakDuration <- dbSendQuery(conCCMooreEarly, statement = paste("SELECT iteration, diseaseduration",
                                                                         "FROM  Results_dailycontrols r",
                                                                         "WHERE 1=1",
                                                                         "AND last_day >0","order by 1"))
      OutDur2<-dbFetch(OutbreakDuration)
 
      #Scenario 3
      
      
      OutbreakDuration <- dbSendQuery(conCCMooreVX21Late, statement = paste("SELECT iteration, diseaseduration",
                                                                          "FROM  Results_dailycontrols r",
                                                                          "WHERE 1=1",
                                                                          "AND last_day >0","order by 1"))
      OutDur3<-dbFetch(OutbreakDuration)
      
      
      #Scenario 4
      
      OutbreakDuration <- dbSendQuery(conCCMooreVxEarly, statement = paste("SELECT iteration, diseaseduration",
                                                                         "FROM  Results_dailycontrols r",
                                                                         "WHERE 1=1",
                                                                         "AND last_day >0","order by 1"))
      OutDur4<-dbFetch(OutbreakDuration)
      
      
      OUTBREAKDUR<-rbind(OutDur,OutDur2,OutDur3,OutDur4)
      OUTBREAKDUR$Scenario<-c(rep("Late",nrow(OutDur)),rep("Early",nrow(OutDur2)),rep("Vx Late",nrow(OutDur3)),rep("Vx Early",nrow(OutDur4)))
      
      
    
       #Scenario 1
      
      TotfarmsOutb<-dbSendQuery(conCCMoore21Late, statement = paste("SELECT iteration, day, last_day, infcU, infcA",
                                                                    "FROM  Results_dailybyproductiontype r",
                                                                    "WHERE 1=1", 
                                                                    "AND production_type_id is null",
                                                                    "and last_day = 1", "order by 1"))
      TFarmOut<-dbFetch(TotfarmsOutb)
      
      
      
      #Scenario 2
      
  
      
      TotfarmsOutb<-dbSendQuery(conCCMooreEarly, statement = paste("SELECT iteration, day, last_day, infcU, infcA",
                                                                   "FROM  Results_dailybyproductiontype r",
                                                                   "WHERE 1=1", 
                                                                   "AND production_type_id is null",
                                                                   "and last_day = 1", "order by 1"))
      TFarmOut2<-dbFetch(TotfarmsOutb)
      
      #Scenario 3
      
      TotfarmsOutb<-dbSendQuery(conCCMooreVX21Late, statement = paste("SELECT iteration, day, last_day, infcU, infcA",
                                                                    "FROM  Results_dailybyproductiontype r",
                                                                    "WHERE 1=1", 
                                                                    "AND production_type_id is null",
                                                                    "and last_day = 1", "order by 1"))
      TFarmOut3<-dbFetch(TotfarmsOutb)
      
      
      
      #Scenario 4
      
      
      
      TotfarmsOutb<-dbSendQuery(conCCMooreVxEarly, statement = paste("SELECT iteration, day, last_day, infcU, infcA",
                                                                   "FROM  Results_dailybyproductiontype r",
                                                                   "WHERE 1=1", 
                                                                   "AND production_type_id is null",
                                                                   "and last_day = 1", "order by 1"))
      TFarmOut4<-dbFetch(TotfarmsOutb)
      
      
      
      TFO<-rbind(TFarmOut,TFarmOut2,TFarmOut3,TFarmOut4)
      TFO$Scenario<-c(rep("Late",nrow(TFarmOut)),rep("Early",nrow(TFarmOut2)),rep("Vx Late",nrow(TFarmOut3)),rep("Vx Early",nrow(TFarmOut4)))
      
      
      
   
      #Scenario 1
      
      farmsDepo<-dbSendQuery(conCCMoore21Late, statement = paste("SELECT iteration, day, last_day, descU, descA",
                                                                 "FROM  Results_dailybyproductiontype r",
                                                                 "WHERE 1=1", 
                                                                 "AND production_type_id is null",
                                                                 "and last_day = 1",
                                                                 "order by 1"))
      
      FarmDepo<-dbFetch(farmsDepo)
    
      
      #Scenario 2
      
      farmsDepo<-dbSendQuery(conCCMooreEarly, statement = paste("SELECT iteration, day, last_day, descU, descA",
                                                                "FROM  Results_dailybyproductiontype r",
                                                                "WHERE 1=1", 
                                                                "AND production_type_id is null",
                                                                "and last_day = 1",
                                                                "order by 1"))
      
      FarmDepo2<-dbFetch(farmsDepo)
      
      #Scenario 3
      
      farmsDepo<-dbSendQuery(conCCMooreVX21Late, statement = paste("SELECT iteration, day, last_day, descU, descA",
                                                                 "FROM  Results_dailybyproductiontype r",
                                                                 "WHERE 1=1", 
                                                                 "AND production_type_id is null",
                                                                 "and last_day = 1",
                                                                 "order by 1"))
      
      FarmDepo3<-dbFetch(farmsDepo)
      
      
      #Scenario 4
      
      farmsDepo<-dbSendQuery(conCCMooreVxEarly, statement = paste("SELECT iteration, day, last_day, descU, descA",
                                                                "FROM  Results_dailybyproductiontype r",
                                                                "WHERE 1=1", 
                                                                "AND production_type_id is null",
                                                                "and last_day = 1",
                                                                "order by 1"))
      
      FarmDepo4<-dbFetch(farmsDepo)
      
   
      
      FD<-rbind(FarmDepo,FarmDepo2,FarmDepo3,FarmDepo4)
      FD$Scenario<-c(rep("Late",nrow(FarmDepo)),rep("Early",nrow(FarmDepo2)),rep("Vx Late",nrow(FarmDepo3)),rep("Vx Early",nrow(FarmDepo4)))
      
      
      #Scenario 3
      VaccUnit3<-dbSendQuery(conCCMooreVX21Late, 
                             statement = paste("SELECT iteration, day, last_day, vaccU",
                                               "FROM  Results_dailybyproductiontype r",
                                               "WHERE 1=1", 
                                               "AND production_type_id is null",
                                               "and last_day = 1", "order by 1"))
      
      #creates the data frame from where analyses will be done
      VaccUnit3<-dbFetch(VaccUnit3) 
      
      #Scenario 4
      VaccUnit4<-dbSendQuery(conCCMooreVxEarly, 
                             statement = paste("SELECT iteration, day, last_day, vaccU",
                                               "FROM  Results_dailybyproductiontype r",
                                               "WHERE 1=1", 
                                               "AND production_type_id is null",
                                               "and last_day = 1", "order by 1"))
      
      #creates the data frame from where analyses will be done
      VaccUnit4<-dbFetch(VaccUnit4) 
      
      VaccUnit<-rbind(VaccUnit3,VaccUnit4)
      VaccUnit$Scenario<-c(rep("Vx Late",nrow(VaccUnit3)),rep("Vx Early",nrow(VaccUnit4)))
      
     
       #using leaflet
      setwd("~/CEAH/ADSM_Missy/R code basics")
      MapMaster<-read.xlsx("MapMaster.xlsx",1)
      
      pal<-colorFactor(c("navy", "red", "green4", "orange", "purple", "pink","brown", "blue"), domain=c("Destruction","Detection","Exam","Exposure","Infection","TraceFound","TraceInitiated","Vaccination"))
      palInf<-colorFactor(c("navy"), domain=c("Infection"))
      
      
      content <- paste(sep = "<br/>",
                       "ID:", MapMaster$ID,
                       "Production Type:", MapMaster$ProductionType,
                       "Size:",MapMaster$UnitSize)
                       
mapWorld = map("world", fill = TRUE, plot = F)# data of world polygon      

```



#Outbreak Characteristics

Add information or description of corresponding outputs

```{r, echo=F}

 #Outbreak Characteristics
    
    EPI<-ggplot(EPICURVE[(EPICURVE$Scenario) %in% params$scenario_variable,],aes(x=day, y=sumInfnU, group=Scenario, colour=Scenario))+
      geom_line(size=1)+
      labs(title="Epidemic Curve",x="Time (days)", y = "New Infected Units")
    
  EPI

  
  
myplot4 <- qplot(Scenario, diseaseDuration, geom=c("boxplot"), data=OUTBREAKDUR[(OUTBREAKDUR$Scenario) %in% params$scenario_variable,],
              fill=Scenario, main="Outbreak duration",
              xlab="", ylab="Duration (days)")
  myplot4 
  
  
  
myplot5 <- qplot(Scenario, infcU, geom=c("boxplot"), data=TFO[(TFO$Scenario) %in% params$scenario_variable,],
              fill=Scenario, main="Farms in outbreak",
              xlab="", ylab="Units")
  myplot5
  

myplot6 <- qplot(Scenario, descU, geom=c("boxplot"), data=FD[(FD$Scenario) %in% params$scenario_variable,],
              fill=Scenario, main="Farms depopulated",
              xlab="", ylab="Units")
  myplot6  

  
myplot6.5 <- qplot(Scenario, vaccU, geom=c("boxplot"), data=VaccUnit[(VaccUnit$Scenario) %in% params$scenario_variable,],
        fill=Scenario, main="Units Vaccinated",
        xlab="", ylab="Farms vaccinated")
    
   myplot6.5
```



#Epidemic Spread

Add information or description of corresponding outputs

```{r, echo=F}
#Epidemic Spread
#Maps with leaflet wont be visible unless is a html file
  
#   # # Reactive expression for the data subsetted to what the user selected
 filteredDataW <- 
     MapMaster[MapMaster$Type=="Infection"& MapMaster$Week ==(params$Week),]

dfW = data.frame(filteredDataW)
m=leaflet(data = mapWorld) %>% addTiles() %>%
  addPolygons(weight = 1, fillColor = "white", color="grey") %>%
 fitBounds(~min(dfW$Lon), ~min(dfW$Lat), ~max(dfW$Lon), ~max(dfW$Lat))
m %>% addCircleMarkers(~Lon, ~Lat, popup=content, radius= ~ifelse(UnitSize,6,10), color = ~palInf(Type), stroke=F, fillOpacity = 0.1, data=dfW)


myplot1 <- qplot(Type, geom=c("bar"), data=MapMaster[(MapMaster$Week)==(params$Week),],
              fill=Type, main="Veterinary Action")+
      theme_void()

 myplot1

  # # Reactive expression for the data subsetted to what the user selected
  filteredDataD <- MapMaster[MapMaster$Type=="Infection" & MapMaster$Day ==(params$Day),]

df = data.frame(filteredDataD)
m=leaflet(data = mapWorld) %>% addTiles() %>%
  addPolygons(weight = 1, fillColor = "white", color="grey") %>%
 fitBounds(~min(df$Lon), ~min(df$Lat), ~max(df$Lon), ~max(df$Lat))
m %>% addCircleMarkers(~Lon, ~Lat, popup=content, radius= ~ifelse(UnitSize,6,10), color = ~palInf(Type), stroke=F, fillOpacity = 0.1, data=df)
  
```



#Herd Level Analyses
 
Add information or description of corresponding outputs
 
```{r, echo=F}

 #Herd Level Analyses
  
myplot7 <- ggplot(Ty[(Ty$Scenario)%in% params$scenario_variable,], aes(x="", y=Freq, fill=Veterinary_action))+
      geom_bar(width = 1, stat = "identity")+
      facet_grid(facets=.~Scenario)+
      xlab("") 
  myplot7
```

```{r, echo=F}

 #Herd Level Analyses Transmission type
  
myplot7.5 <-ggplot(Tran[(Tran$Scenario)%in% params$scenario_variable,], aes(x="", y=Freq, fill=Transmission))+
      geom_bar(width = 1, stat = "identity")+
      facet_grid(facets=.~Scenario)+
      xlab("") 
    
  myplot7.5
```


##Netwrok visualization

```{r, echo=F}


  par(mfrow = c(1, length(params$scenario_variable)))
    
    for (i in 1:length(params$scenario_variable)){
      
      net2<-graph.data.frame(daily_graphdatprep[daily_graphdatprep$Scenario == params$scenario_variable[i],],directed=F)#specified edges of a directed farm "Early"
      
      
      
      plot(net2, layout=layout.fruchterman.reingold, vertex.size=8,edge.arrow.size=0.5, vertex.label=NA, main=params$scenario_variable[i])
      
          }
    
        par(mfrow = c(1, 1))

```

