---
title: "Report.Rmd"
author: "Karla Moreno"
date: "February 7, 2018"
output:
  html_document: default
  word_document: default
  pdf_document: default
params:
    scenario_variable: NA
    Week: NA
    Day: NA
always_allow_html: yes
---

# Dynamic Report

# Creating a document that provides comparison of disease modeling scenarios ran in ADSM. 

We created an R Markdown document that would guide the R user to explore the outputs from ADSM by modifying or expanding this basic code. 

# Background about the simulation modeling of infectious diseases

Describe the population, location, and disease studied, including the baseline mechanisms of transmission and control strategies that are included in each of the scenarios.

## List of scenarios 
In our example below, we will visualize outputs of two scenarios. Scenarios are simulations of disease spread where factors are modified from the baseline scenario in order to better understand its effect on the outbreak characteristics. 


# Outbreak Characteristics

Add information or description of corresponding outputs

```{r, echo=F}

 #Outbreak Characteristics
    
    EPI<-ggplot(dbtable$epiCur[(dbtable$epiCur$Scenario) %in% params$scenario_variable,],aes(x=day, y=sumInfnU, group=Scenario, colour=Scenario))+
      geom_line(size=1)+
      labs(title="Epidemic Curve",x="Time (days)", y = "New Infected Units")
    
  EPI

  
  
myplot4 <- qplot(Scenario, diseaseDuration, geom=c("boxplot"), data=dbtable$outDur[(dbtable$outDur$Scenario) %in% params$scenario_variable,],
              fill=Scenario, main="Outbreak duration",
              xlab="", ylab="Duration (days)")
  myplot4 
  
  
  
myplot5 <- qplot(Scenario, infcU, geom=c("boxplot"), data=dbtable$tFarmOut[(dbtable$tFarmOut$Scenario) %in% params$scenario_variable,],
              fill=Scenario, main="Farms in outbreak",
              xlab="", ylab="Units")
  myplot5
  

myplot6 <- qplot(Scenario, descU, geom=c("boxplot"), data=dbtable$farmDepo[(dbtable$farmDepo$Scenario) %in% params$scenario_variable,],
              fill=Scenario, main="Farms depopulated",
              xlab="", ylab="Units")
  myplot6  

  
myplot6.5 <- qplot(Scenario, vaccU, geom=c("boxplot"), data=dbtable$vaccUnit[(dbtable$vaccUnit$Scenario) %in% params$scenario_variable,],
        fill=Scenario, main="Units Vaccinated",
        xlab="", ylab="Farms vaccinated")
    
   myplot6.5
```



# Epidemic Spread

Add information or description of corresponding outputs

```{r, echo=F}
#Epidemic Spread
#Maps with leaflet wont be visible unless is a html file
  
#   # # Reactive expression for the data subsetted to what the user selected
 filteredDataW <- 
     MapMaster[MapMaster$Type=="Infection"& MapMaster$Week ==(params$Week),]

dfW = data.frame(filteredDataW)
m=leaflet(data = mapWorld) %>% addTiles() %>%
  addPolygons(weight = 1, fillColor = "white", color="grey") %>%
 fitBounds(~min(dfW$Lon), ~min(dfW$Lat), ~max(dfW$Lon), ~max(dfW$Lat))
m %>% addCircleMarkers(~Lon, ~Lat, popup=content, radius= ~ifelse(UnitSize,6,10), color = ~palInf(Type), stroke=F, fillOpacity = 0.1, data=dfW)


myplot1 <- qplot(Type, geom=c("bar"), data=MapMaster[(MapMaster$Week)==(params$Week),],
              fill=Type, main="Veterinary Action")+
      theme_void()

 myplot1

  # # Reactive expression for the data subsetted to what the user selected
  filteredDataD <- MapMaster[MapMaster$Type=="Infection" & MapMaster$Day ==(params$Day),]

df = data.frame(filteredDataD)
m=leaflet(data = mapWorld) %>% addTiles() %>%
  addPolygons(weight = 1, fillColor = "white", color="grey") %>%
 fitBounds(~min(df$Lon), ~min(df$Lat), ~max(df$Lon), ~max(df$Lat))
m %>% addCircleMarkers(~Lon, ~Lat, popup=content, radius= ~ifelse(UnitSize,6,10), color = ~palInf(Type), stroke=F, fillOpacity = 0.1, data=df)
  
```



# Herd Level Analyses
 
Add information or description of corresponding outputs
 
```{r, echo=F}

 #Herd Level Analyses
  
myplot7 <- ggplot(daily_compare[(daily_compare$Scenario)%in% params$scenario_variable,], aes(x="", y=Freq, fill=Veterinary_action))+
      geom_bar(width = 1, stat = "identity")+
      facet_grid(facets=.~Scenario)+
      xlab("") 
  myplot7
```

```{r, echo=F}

 #Herd Level Analyses Transmission type
  
myplot7.5 <-ggplot(daily_comparE[(daily_comparE$Scenario)%in% params$scenario_variable,], aes(x="", y=Freq, fill=Transmission))+
      geom_bar(width = 1, stat = "identity")+
      facet_grid(facets=.~Scenario)+
      xlab("") 
    
  myplot7.5
```


## Network visualization

```{r, echo=F}


  par(mfrow = c(1, length(params$scenario_variable)))
    
    for (i in 1:length(params$scenario_variable)){
      
      net2<-graph.data.frame(daily_graphdatprep[daily_graphdatprep$Scenario == params$scenario_variable[i],],directed=F)#specified edges of a directed farm "Early"
      
      
      
      plot(net2, layout=layout.fruchterman.reingold, vertex.size=8,edge.arrow.size=0.5, vertex.label=NA, main=params$scenario_variable[i])
      
          }
    
        par(mfrow = c(1, 1))

```

